### 2017-06-13 Docs/Thesis/docs/chapter4.tex
text

>>>>

In this chapter we are going to go in deep details on some implementations and modelling approaches mentioned in the last chapter.

In the frist section, we are going to discuss our methodology for modelling inter pacekt times, and validade it as a good choise. The problem we want to adress are these one:

\begin{itemize}

	\item We have a set of empirical inter-packet times, and some aproximate stochastic models that describe it. We want to know what is the best, in a analyctical way.

	\item We whant to know whatever if our modelling aproaches are good ot not to describe inter pacekt times.

\end{itemize}

Many works have been made in second point on the literature, but not so many on the second. So we are proposing a model, and validating it.

In the second section, we will describe breifely two others we used to calc flow's session ON and OFF times, and
